### 2016-11-07 paper3.tex
Added short captions for tables
Added all TOC elements
Fixed page numbering
Fixed figure sizes

\begin{abstract}

@@

\subsection{Superbubble Feedback}
\begin{table*}
\input{figures3/z0_table.tex}
\caption{Redshift 0 properties of the full MUGS2 sample.  All masses and
    particle counts are measured within a $R_{\rm vir}$ sphere centred on the halo, except for
$M_{\rm central}$, which is measured within a $0.1\;R_{\rm vir}$ sphere.}
\label{z0_table}
\end{table*}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/stellar_edge.eps}
    \includegraphics[width=\textwidth]{figures3/stellar_face.eps}
    \caption[Mock stellar images of MUGS2 galaxies]{Mock optical stellar
    observations of each MUGS2 galaxy.  RGB channels are calculated using
    \citet{Marigo2008} stellar populations.  The top three rows show the
    galaxies edge on, while the bottom three show the galaxies face on.  The
    galaxies are sorted in order of halo mass, and galaxies that overproduce
    stars are labelled with red.  These images do not include the effects of
    dust extinction}
    \label{stellar_image}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/column_edge.eps}
    \includegraphics[width=\textwidth]{figures3/column_face.eps}
    \caption[HI column density images for MUGS2 galaxies]{{\sc Hi} column
    density in each of the MUGS2 galaxies.  As in Fig.~\ref{stellar_image}, the
    top three rows show the galaxy edge on.}
    \label{gas_column}
\end{figure*}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/SMHMR.eps}
    \caption[MUGS2 stellar mass to halo mass relation]{Stellar mass versus halo
    mass at $z=0$.  The observed stellar mass to halo mass relation is from
    \citet{Hudson2015}'s weak lensing study of galaxies to $z=0.8$.  Galaxies
    that fall within this range are shown as blue squares, while galaxies above
    the curve (those which form too many stars) are shown as red circles.  For
    comparison, the black stars show galaxies from the NIHAO sample
    \citep{Wang2015}.}
    \label{SMHMR}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/rotcurve.eps}
    \caption[MUGS2 rotation curves]{As is clear from the above rotation curves,
    galaxies which overproduce stars (shown in dotted red) also have large
    central concentrations, giving steeply peaked rotation curves inconsistent
    with those seen in local $L*$ galaxies.  Galaxies with well-regulated star
    formation have flat rotation curves (shown in solid blue).}
    \label{rotation_curve}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/stellar_central.eps}
    \caption[Stellar mass vs. central baryonic mass in MUGS2 galaxies]{The stellar mass and the central baryonic mass show a tight
        correlation.  For the well-regulated population, roughly $40\%$ of the
        central baryons are stars, while for the unregulated population has
        converted $\sim70\%$ of the central baryon mass into stars.}
    \label{stellar_central}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/phase.eps}
    \caption[Gas phase diagram in two MUGS2 galaxies]{Gas phase diagrams for a
    well-regulated galaxy (g24334) and an unregulated galaxy (g19195).  Colour
    shows the amount of mass at a given $\rho-T$ point.  The top phase diagram
    shows the characteristic slope for adiabatic (dashed line) and isobaric
    (dotted line) processes.  As can be seen, both galaxies are qualitatively
    the same.  Both show the equilibrium cooling curve below $10^4\K$, and both
    show the adiabatic evolution of superbubble-heated gas as it leaves the
    disc.}
    \label{phase}
\end{figure}

@@

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/stellar_fraction_time.eps}
    \caption[Stellar mass fraction evolution in MUGS2]{Stellar mass fraction
    versus time.  As is clear, for the unregulated population the buildup of
    stellar mass above $\sim3\%$ of the halo mass happens very rapidly, often on
    time-scales of $\sim1\Gyr$.  The runaway in the unregulated population stops
    simply when the disc has been sufficiently depleted of gas that little
    remains to form new stars.}
    \label{stellar_fraction_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/SMHMR_time.eps}
    \caption[Stellar mass vs. halo mass evolution in MUGS2]{Stellar mass versus
    halo mass, as shown in Fig.~\ref{SMHMR}, but with trails added to show time
    evolution.  For halo masses below $\sim\rm{a\;few}\times10^{11}$, the
    evolution of the regulated and unregulated populations are
    indistinguishable.  The grey bar shows the $z=0$ SMHMR, as in
    Fig.~\ref{SMHMR}}
    \label{SMHMR_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/stellar_central_time.eps}
    \caption[Stellar mass vs. central baryonic mass evolution in MUGS2]{Stellar
    mass versus central baryon mass. The stellar mass here can be seen to vary
    much more smoothly over the evolution, without the slight `jump' seen in
    Fig.~\ref{stellar_fraction_time}.}
    \label{stellar_central_time}
\end{figure}

@@

\subsection{Galactic Outflows}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_time.eps}
    \caption[Outflow mass loading evolution in MUGS2]{Outflow mass loading
    decreases as galaxies grow over time, as was previously shown by
    \citet{Keller2015}.  Here we see, when examining the mean mass loadings for
    the two populations (the well-regulated galaxies, where stellar feedback
    succeeds, and the unregulated galaxies, where it fails), that the
    unregulated galaxies have their mass loadings decrease sooner, and to lower
    values, than the well-regulated population.  The error bars here are the
    $1\sigma$ scatter in each population.}
    \label{massloading_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_halo.eps}
    \caption[Mass loading as a function of halo mass in MUGS2]{Unlike in the
    previous figure, if we look at mass loading as a function of halo mass, we
    instead see no significant difference between the two populations.  Instead,
    both follow a similar trajectory, and the haloes which fail to self-regulate
    do so simply because they reach a higher mass earlier.}
    \label{massloading_halo}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_central.eps}
    \caption[Mass loadings as a function of disc mass]{The mass loadings of the two populations are even more in agreement
    if we look at their relation to the central baryonic mass.  As with the mass
    loading versus halo mass relation, we can fit a broken power law to this relation
    (shown here as the dashed line).}
    \label{massloading_central}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/coldmassloading.eps}
    \caption[Outflow mass loading for cold and hot gas]{Mean outflow mass loading for the full sample, as a function of
    halo mass/virial temperature, and split into cold ($T<10^5\K$) and hot
    ($T>10^5\K$) components.  For low-mass haloes, outflows are dominated by
    relatively cold gas (cooler superbubbles, and entrained material), while heavier
    haloes have primarily hot outflows.  The transition occurs at a halo mass of
    $M_{\rm halo}\sim10^{11}\;\Msun$, or a virial temperature of $6\times10^5\K$.}
    \label{coldmassloading}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_escape.eps}
    \caption[Mass loading vs. escape velocity of disc]{Mean outflow mass loading for the full sample, as a function of the
        escape velocity on the inner surface of our outflow shell
        ($0.1R_{\rm vir}$).  Each galaxy is sampled 128 times over its evolution,
        giving us 2304 points across a range of redshifts.  As can be seen, at
        $v_{\rm esc}\sim 250\;km/s$, the mass loading begins to fall precipitously.
        This corresponds to the sound speed of solar-metallicity gas at a
        temperature of $3.5\times10^{6}\K$.  This means that for gas at or
        above this temperature, sound waves alone are able to propel material
        significantly above the disc, and that kinetic energy losses due to
        shocks will be minimal.  Gas cooler than that will need to be propelled
        supersonically, and will drive shocks in the CGM.}
    \label{massloading_escape}
\end{figure}

>>>>

\setcounter{pageFix}{\value{page}}
\begin{abstract}
    \setcounter{page}{\value{pageFix}}
        \addcontentsline{toc}{section}{Abstract}

@@

\subsection{Superbubble Feedback}
\begin{table*}
\input{figures3/z0_table.tex}
    \caption[Summary of MUGS2 galaxy properties]{Redshift 0 properties of the
    full MUGS2 sample.  All masses and particle counts are measured within a
    $R_{\rm vir}$ sphere centred on the halo, except for $M_{\rm central}$,
    which is measured within a $0.1\;R_{\rm vir}$ sphere.}
\label{z0_table}
\end{table*}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/stellar_edge.eps}
    \includegraphics[width=\textwidth]{figures3/stellar_face.eps}
    \caption[Mock stellar images of MUGS2 galaxies]{Mock optical stellar
    observations of each MUGS2 galaxy.  RGB channels are calculated using
    \citet{Marigo2008} stellar populations.  The top three rows show the
    galaxies edge on, while the bottom three show the galaxies face on.  The
    galaxies are sorted in order of halo mass, and galaxies that overproduce
    stars are labelled with red.  These images do not include the effects of
    dust extinction}
    \label{stellar_image}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/column_edge.eps}
    \includegraphics[width=\textwidth]{figures3/column_face.eps}
    \caption[HI column density images for MUGS2 galaxies]{{\sc Hi} column
    density in each of the MUGS2 galaxies.  As in Fig.~\ref{stellar_image}, the
    top three rows show the galaxy edge on.}
    \label{gas_column}
\end{figure*}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/SMHMR.eps}
    \caption[MUGS2 stellar mass to halo mass relation]{Stellar mass versus halo
    mass at $z=0$.  The observed stellar mass to halo mass relation is from
    \citet{Hudson2015}'s weak lensing study of galaxies to $z=0.8$.  Galaxies
    that fall within this range are shown as blue squares, while galaxies above
    the curve (those which form too many stars) are shown as red circles.  For
    comparison, the black stars show galaxies from the NIHAO sample
    \citep{Wang2015}.}
    \label{SMHMR}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/rotcurve.eps}
    \caption[MUGS2 rotation curves]{As is clear from the above rotation curves,
    galaxies which overproduce stars (shown in dotted red) also have large
    central concentrations, giving steeply peaked rotation curves inconsistent
    with those seen in local $L*$ galaxies.  Galaxies with well-regulated star
    formation have flat rotation curves (shown in solid blue).}
    \label{rotation_curve}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/stellar_central.eps}
    \caption[Stellar mass vs. central baryonic mass in MUGS2 galaxies]{The stellar mass and the central baryonic mass show a tight
        correlation.  For the well-regulated population, roughly $40\%$ of the
        central baryons are stars, while for the unregulated population has
        converted $\sim70\%$ of the central baryon mass into stars.}
    \label{stellar_central}
\end{figure}
\begin{figure}
    \includegraphics[width=0.63\textwidth]{figures3/phase.eps}
    \caption[Gas phase diagram in two MUGS2 galaxies]{Gas phase diagrams for a
    well-regulated galaxy (g24334) and an unregulated galaxy (g19195).  Colour
    shows the amount of mass at a given $\rho-T$ point.  The top phase diagram
    shows the characteristic slope for adiabatic (dashed line) and isobaric
    (dotted line) processes.  As can be seen, both galaxies are qualitatively
    the same.  Both show the equilibrium cooling curve below $10^4\K$, and both
    show the adiabatic evolution of superbubble-heated gas as it leaves the
    disc.}
    \label{phase}
\end{figure}

@@

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/stellar_fraction_time.eps}
    \caption[Stellar mass fraction evolution in MUGS2]{Stellar mass fraction
    versus time.  As is clear, for the unregulated population the buildup of
    stellar mass above $\sim3\%$ of the halo mass happens very rapidly, often on
    time-scales of $\sim1\Gyr$.  The runaway in the unregulated population stops
    simply when the disc has been sufficiently depleted of gas that little
    remains to form new stars.}
    \label{stellar_fraction_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/SMHMR_time.eps}
    \caption[Stellar mass vs. halo mass evolution in MUGS2]{Stellar mass versus
    halo mass, as shown in Fig.~\ref{SMHMR}, but with trails added to show time
    evolution.  For halo masses below $\sim\rm{a\;few}\times10^{11}$, the
    evolution of the regulated and unregulated populations are
    indistinguishable.  The grey bar shows the $z=0$ SMHMR, as in
    Fig.~\ref{SMHMR}}
    \label{SMHMR_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/stellar_central_time.eps}
    \caption[Stellar mass vs. central baryonic mass evolution in MUGS2]{Stellar
    mass versus central baryon mass. The stellar mass here can be seen to vary
    much more smoothly over the evolution, without the slight `jump' seen in
    Fig.~\ref{stellar_fraction_time}.}
    \label{stellar_central_time}
\end{figure}

@@

\subsection{Galactic Outflows}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/massloading_time.eps}
    \caption[Outflow mass loading evolution in MUGS2]{Outflow mass loading
    decreases as galaxies grow over time, as was previously shown by
    \citet{Keller2015}.  Here we see, when examining the mean mass loadings for
    the two populations (the well-regulated galaxies, where stellar feedback
    succeeds, and the unregulated galaxies, where it fails), that the
    unregulated galaxies have their mass loadings decrease sooner, and to lower
    values, than the well-regulated population.  The error bars here are the
    $1\sigma$ scatter in each population.}
    \label{massloading_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/massloading_halo.eps}
    \caption[Mass loading as a function of halo mass in MUGS2]{Unlike in the
    previous figure, if we look at mass loading as a function of halo mass, we
    instead see no significant difference between the two populations.  Instead,
    both follow a similar trajectory, and the haloes which fail to self-regulate
    do so simply because they reach a higher mass earlier.}
    \label{massloading_halo}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures3/massloading_central.eps}
    \caption[Mass loadings as a function of disc mass]{The mass loadings of the two populations are even more in agreement
    if we look at their relation to the central baryonic mass.  As with the mass
    loading versus halo mass relation, we can fit a broken power law to this relation
    (shown here as the dashed line).}
    \label{massloading_central}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/coldmassloading.eps}
    \caption[Outflow mass loading for cold and hot gas]{Mean outflow mass loading for the full sample, as a function of
    halo mass/virial temperature, and split into cold ($T<10^5\K$) and hot
    ($T>10^5\K$) components.  For low-mass haloes, outflows are dominated by
    relatively cold gas (cooler superbubbles, and entrained material), while heavier
    haloes have primarily hot outflows.  The transition occurs at a halo mass of
    $M_{\rm halo}\sim10^{11}\;\Msun$, or a virial temperature of $6\times10^5\K$.}
    \label{coldmassloading}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/massloading_escape.eps}
    \caption[Mass loading vs. escape velocity of disc]{Mean outflow mass loading for the full sample, as a function of the
        escape velocity on the inner surface of our outflow shell
        ($0.1R_{\rm vir}$).  Each galaxy is sampled 128 times over its evolution,
        giving us 2304 points across a range of redshifts.  As can be seen, at
        $v_{\rm esc}\sim 250\;km/s$, the mass loading begins to fall precipitously.
        This corresponds to the sound speed of solar-metallicity gas at a
        temperature of $3.5\times10^{6}\K$.  This means that for gas at or
        above this temperature, sound waves alone are able to propel material
        significantly above the disc, and that kinetic energy losses due to
        shocks will be minimal.  Gas cooler than that will need to be propelled
        supersonically, and will drive shocks in the CGM.}
    \label{massloading_escape}
\end{figure}
